Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-17 paper.tex
rough draft related work

\author{Stefan Mühlbauer}
\affiliation{%
  \institution{Technische Universität Braunschweig}
  %\streetaddress{P.O. Box 1212}
  %\city{Braunschweig} 
  %\state{Germany} 
  %\postcode{43017-6221}
}
%\email{s.muehlbauer@tu-bs.de}

\author{Christian Kästner}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{Carnegie Mellon University}
  %\streetaddress{5000 Forbes Avenue}
  %\city{Pittsburgh} 
  %\state{PA} 
  %\postcode{15217}
}
%\email{s.muehlbauer@tu-bs.de}

\author{Tien N. Nguyen}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{University of Texas at Dallas}
  %\streetaddress{P.O. Box 1212}
  %\city{Braunschweig} 
  %\state{Germany} 
  %\postcode{43017-6221}
}
%\email{s.muehlbauer@tu-bs.de}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{\textcolor{blue}{put shortauthors here}}

@@

	\item \emph{Varis}: Editor services such as “jump to declaration” are
	nontrivial for dynamic web applications due to their staged nature. Varis
	provides editor services across stages for client-side code: Starting with an
	ouput approximation a callgraph with conditional edges is constructed, which
	allows navigation in client-site code (HTML, JS and CSS) although it is
	embedded in server-side code
	\cite{Nguyen:2015:VIS:2819009.2819140,Nguyen:2014:BCG:2635868.2635928}.
\end{itemize}

@@

\paragraph{Bypassing conceptual limitations.}
Symbolic execution is used to approximate client page output since it allows to
unfold the staged nature of dynamic web applications. Aside from conceptual
limitations in the systems studied, limitations can be addressed. To use
approaches incorporating symbolic execution with dynamic web applications in
the long run, more concrete dummy information, similar to test oracles, needs
to be provided to decrease the number of assumed symbolic inputs and avoid
dynamic features being confronted with symbolic values.Also, if the usage of
tools using static output approximation with symbolic execution is intended,
avoiding dynamic features that are prone to be inaccurately executed for
symbolic execution  may be an adjustment strategy to program in an analyzable
way.

@@

\section{Related Work} \label{sec:related_work}
\cite{Hills:2013:ESP:2483760.2483786}
\cite{wassermann2007sound,minamide2005static}
%\textcolor{blue}{\blindtext}

>>>>

%\author{Stefan Mühlbauer}
\affiliation{%
  %\institution{Technische Universität Braunschweig}
  %\streetaddress{P.O. Box 1212}
  %\city{Braunschweig} 
  %\state{Germany} 
  %\postcode{43017-6221}
}
%\email{s.muehlbauer@tu-bs.de}

%\author{Christian Kästner}
%\orcid{1234-5678-9012}
\affiliation{%
  %\institution{Carnegie Mellon University}
  %\streetaddress{5000 Forbes Avenue}
  %\city{Pittsburgh} 
  %\state{PA} 
  %\postcode{15217}
}
%\email{s.muehlbauer@tu-bs.de}

%\author{Tien N. Nguyen}
%\orcid{1234-5678-9012}
\affiliation{%
  %\institution{University of Texas at Dallas}
  %\streetaddress{P.O. Box 1212}
  %\city{Braunschweig} 
  %\state{Germany} 
  %\postcode{43017-6221}
}
%\email{s.muehlbauer@tu-bs.de}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{
	%\textcolor{blue}{put shortauthors here}
}

@@

	\item \emph{Varis}: Editor services such as “jump to declaration” are
	nontrivial for dynamic web applications due to their staged nature. Varis
	provides editor services across stages for client-side code: Starting with an
	ouput approximation a callgraph with conditional edges is constructed, which
	allows navigation in client-site code (HTML, JS and CSS) although it is
	embedded in server-side code
	\cite{Nguyen:2015:VIS:2819009.2819140,Nguyen:2014:BCG:2635868.2635928}.

\end{itemize}

@@

\paragraph{Bypassing conceptual limitations.}
Symbolic execution is used to approximate client page output since it allows to
unfold the staged nature of dynamic web applications. Aside from conceptual
limitations in the systems studied, limitations can be addressed. To use
approaches incorporating symbolic execution with dynamic web applications in
the long run, more concrete dummy information, similar to test oracles, needs
to be provided to decrease the number of assumed symbolic inputs and avoid
dynamic features being confronted with symbolic values. Also, if the usage of
tools using static output approximation with symbolic execution is intended,
avoiding dynamic features that are prone to be inaccurately executed for
symbolic execution  may be an adjustment strategy to program in an analyzable
way. 
Future work to increase code coverage and approximation quality might involve
automated test case generation as tools like \sf{Apollo}
\cite{artzi_finding_2008,artzi_finding_2010} or previous
work \cite{DynamicWassermann} to decrease the number of symbolic inputs and
provide proper and concrete input variants.

@@

\section{Related Work} \label{sec:related_work}
\paragraph{Static Output Approximation}
To approximate program slices for web
applications, Ricca et al. \cite{tonella_web_2005,tonella_2001,tonella_2002} approximate
dynamically generated output. For output generating statements, such as \tt{echo} or
\tt{print}, all strings are unquoted (code extrusion). If those statements
contain variables, these are linked to string concatenations using a
proposed flow analysis called \emph{string-cat propagation}. From these
flows representing approximated output subsequent program slices are computed.

Minamide \cite{minamide_static_2005} approximates client page output
of web applications by describing possible output by a context-free
grammar that is constructed statically from the PHP code for a given regular
expression of user input. The constructed grammar enables analyses such as
detecting cross-site scripting vulnerabilities by checking whether user input has been sanitized, and HTML validation by
determining whether the constructed grammar is contained in a depth-bound
HTML grammar. Based on Minamide's approximation approach several
vulnerability analyses addressing cross-site scripting
\cite{wassermann_static_2008} and SQL injection \cite{wassermann2007sound} have
been proposed. Wang et al. \cite{wang_locating_2010} utilizes this string analysis to detect strings visible at the browser and enable
internationalization of web applications.

Another approach is proposed by Wang et al. \cite{wang_automating_2012}, where
output for a web application is approximated using a hybrid approach: A
dynamic webpage is executed with concrete input and the execution is
recorded at runtime. Changes in the client-side output then can be mapped to 
corresponding PHP code using static impact analysis.

%Creating Test Input \cite{DynamicWassermann}

Something about dynamic features and resolution
  \cite{Hills:2013:ESP:2483760.2483786,hills2014static,hills2015variable}

Tools using symbolic execution for static output approximation
   \cite{artzi_finding_2008,artzi_finding_2010}
%\textcolor{blue}{\blindtext}
